\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-14 doc/flexiblesusy-paper.tex
address referee 1 comment 4b: SUSY model restrictions
Added comments about the supported gauge groups and Yukawa coupling
structure at low energies.

@@

Afterwards, SARAH's expression for the Weinberg angle $\theta_W$ in
terms of $M_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$,
$M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)$ is used to calculate
$\theta_W$ in the SUSY model in the \DRbar\ scheme.  In the MSSM, for
example, it yields

@@

triplet field.

@@

At the low-scale the \DRbar\ Yukawa coupling matrices
$y_f^{\text{\DRbar}}(M_Z)$ ($f=u,d,e$) in the SUSY model are
calculated automatically if the user has set $y_f$ to the value
\code{Automatic} in the \fs model file.  This is done for example in

>>>>

The low-scale constraint matches the SUSY model to the Standard Model.
Currently \fs allows only SUSY models with semisimple gauge groups,
which contain the Standard Model gauge group $\SUc\times\SUL\times\UY$
as factor.  This enables \fs to directly identify the strong,
left-handed and hypercharge gauge couplings $g_i$ ($i=1,2,3$).

@@

Afterwards, the user-defined expression for the Weinberg angle
$\theta_W$ in terms of $M_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$ and
$M_{Z,\text{susy}}^{\text{\DRbar}}(M_Z)$ (defined by the user in the
SARAH model file) is used to calculate $\theta_W$ in the SUSY model in
the \DRbar\ scheme.  In the MSSM, for example, it yields

@@

triplet field.  In models with an additional $U(1)'$ gauge group, the
additional $Z'$ gauge boson can mix with the $Z$ boson.  In such
models the Weinberg angle can be defined by parametrizing the
$Z$--$Z'$ mixing matrix as
  \begin{pmatrix}
    \cos\theta_W & -\sin\theta_W \cos\theta_W' &  \sin\theta_W \sin\theta_W' \\
    \sin\theta_W &  \cos\theta_W \cos\theta_W' & -\cos\theta_W \sin\theta_W' \\
    0 & \sin\theta_W' & \cos\theta_W'
  \end{pmatrix},
where $\theta_W'$ is the $Z$--$Z'$ mixing angle.

@@

The considered SUSY model is required to contain the three generations
of Standard Model quarks and leptons.  If these particles acquire
their masses due to Yukawa interactions with Higgs doublets, then the
$3\times 3$ Yukawa matrices $y_f$ ($f=u,d,e$) can be calculated
automatically in the \DRbar\ scheme at the scale $M_Z$ from the known
Standard Model fermion masses by setting $y_f$ to the value
\code{Automatic} in the \fs model file.
This is done for example in
